\documentclass{article}
\usepackage{geometry}
\geometry{margin=1in}
\begin{document}

\title{Perforce Tutorial Quizzes and Answers}
\author{}
\date{}

\maketitle

\section*{Quiz 1: Basic Commands}

\subsection*{Question 1}

Which command do you use to retrieve the latest files from the depot to your workspace?

\begin{enumerate}
    \item \texttt{p4 update}
    \item \texttt{p4 fetch}
    \item \texttt{p4 sync}
    \item \texttt{p4 get}
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} \texttt{p4 sync} (\textbf{Option C})

\hrulefill

\subsection*{Question 2}

How do you open a file for editing?

\begin{enumerate}
    \item \texttt{p4 open}
    \item \texttt{p4 edit}
    \item \texttt{p4 modify}
    \item \texttt{p4 change}
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} \texttt{p4 edit} (\textbf{Option B})

\hrulefill

\section*{Quiz 2: Concepts}

\subsection*{Question 3}

What is a changelist in Perforce?

\begin{enumerate}
    \item A list of clients connected to the server.
    \item A collection of file revisions submitted as a single unit.
    \item A history log of all changes.
    \item A backup of the depot.
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} A collection of file revisions submitted as a single unit. (\textbf{Option B})

\hrulefill

\subsection*{Question 4}

True or False: The \texttt{p4 integrate} command is used only for merging changes, not for creating branches.

\subsubsection*{Answer}

\textbf{Answer:} False. The \texttt{p4 integrate} command is used for both branching and merging.

\hrulefill

\section*{Quiz 3: Advanced Usage}

\subsection*{Question 5}

Which command would you use to revert all unchanged files in a pending changelist?

\begin{enumerate}
    \item \texttt{p4 revert -a}
    \item \texttt{p4 clean}
    \item \texttt{p4 undo}
    \item \texttt{p4 discard}
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} \texttt{p4 revert -a} (\textbf{Option A})

\hrulefill

\subsection*{Question 6}

What is the purpose of shelving in Perforce?

\begin{enumerate}
    \item To permanently delete files from the depot.
    \item To submit changes to the depot.
    \item To temporarily store changes on the server without submitting.
    \item To clone a repository.
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} To temporarily store changes on the server without submitting. (\textbf{Option C})

\hrulefill

\section*{Quiz 4: Practical Scenario}

\subsection*{Question 7}

Alice and Bob are both working on \texttt{file1.txt}. Alice submits her changes before Bob. When Bob tries to submit, he gets an error about conflicting revisions. What should Bob do?

\begin{enumerate}
    \item Force submit his changes.
    \item Revert his changes.
    \item Use \texttt{p4 sync} followed by \texttt{p4 resolve}.
    \item Delete the file.
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} Use \texttt{p4 sync} followed by \texttt{p4 resolve}. (\textbf{Option C})

\hrulefill

\subsection*{Question 8}

How can you view the revision history of a file?

\begin{enumerate}
    \item \texttt{p4 history filename}
    \item \texttt{p4 log filename}
    \item \texttt{p4 filelog filename}
    \item \texttt{p4 revisions filename}
\end{enumerate}

\subsubsection*{Answer}

\textbf{Answer:} \texttt{p4 filelog filename} (\textbf{Option C})

\hrulefill

\end{document}
